Storing messages with multipartite neural cliques

### 2014-07-10 Articles/article.tex
...

	Each message $x = (x_i)_{1 \le i \le c}$ is mapped to $y = (y_i)_{1 \le i \le c}$ where $y_i$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).

@@

		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$).
		The following is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
		\begin{algorithm}
		\caption{$w$-sum of sum \label{asumsum}}

		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to S}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	%edge : $(i, j)$
	Suppose we are trying to recover a message where $c_e$ clusters have been erased.

@@

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
			\label{erasuresth}
		\end{figure}

@@

	\subsubsection{Analytical result}	
%	Formula for errors instead of erasures : 
%	
%	gc : good (à remplacer par right/wrong ?) neuron in correct cluster
%	
%	ge : good neuron in erroneous cluster
%	
%	abe : bad activated neuron in erroneous cluster
%	
%	be : others bad (à remplacer par wrong ou incorrect etc.) neurons in erroneous cluster
%	
%	bc : bad neuron in correct cluster
	Messages can be corrupted, our models for errors is : fix $c_e$ the number of erroneous clusters, we draw at random $c_e$ clusters and in each of these draw at random, uniformly, a new letter in the alphabet that will replace the old one (it could be the same).

@@

	Our deviation model is the same as \cite{LedGriRabGro20145}\footnote{Compared to this article, we do not draw at random a letter in case of ambiguity, which hurts performance a bit.}, that is random binary noise on edges.

@@

	Figure \ref{comppsi} seems to indicate a linear relationship (after a transition for multiple activities) between $\eta_\psi -\eta_0$ and $\psi$.
	\section{Maximum theoretical efficiency}
		It was shown in \cite{oo}, asymptotic capacities of clique networks is $\log 2$. We generalise this result to multipartite cliques.

@@

		Fixing $k^* = -\frac{a^2}{2} \log_2 (d)$ gives us $\eta \sim \log_2 d \log_2 (1-d) \log 2$ and therefore \[\eta_{max} = \log 2\]

@@

	%Marche mieux pouur de petits c --> le faire sur le sparse ?

>>>>

	Each message $x = (x_i)_{1 \le i \le c}$ is mapped to $y = (y_i)_{1 \le i \le c}$ where $y_i$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).\footnote{This is a local code of constant-weight $a$.}

@@

		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$).
		The following is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
		\begin{algorithm}
		\caption{$w$-sum of sum \label{asumsum}}
		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to S}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	%edge : $(i, j)$
	We generalise results on erasures obtained in \cite{GriBer20117} to multipartie cliques.

	Suppose we are trying to recover a message where $c_e$ clusters have been erased.

@@

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
			\label{erasuresth}
		\end{figure}

@@

	\subsubsection{Analytical result}
%	Formula for errors instead of erasures : 
%	
%	gc : good (à remplacer par right/wrong ?) neuron in correct cluster
%	
%	ge : good neuron in erroneous cluster
%	
%	abe : bad activated neuron in erroneous cluster
%	
%	be : others bad (à remplacer par wrong ou incorrect etc.) neurons in erroneous cluster
%	
%	bc : bad neuron in correct cluster

	We provide a formula for error rate in case of messages with corrupted clusters.

	Messages can be corrupted, our models for errors is : given $c_e$ the number of erroneous clusters, we draw at random $c_e$ clusters and in each of these draw at random, uniformly, a new letter in the alphabet that will replace the old one (it could be the same).

@@

	Our deviation model is the same as \cite{LedGriRabGro20145}\footnote{Compared to this article, we do not draw at random a letter in case of ambiguity, which hurts performance a bit.}, that is random binary noise on edges. We generalise results of \cite{LedGriRabGro20145} to multipartite cliques.

@@

	Figure \ref{comppsi} seems to indicate a linear relationship (after a transition for multiple activities) between $\eta_\psi -\eta_0$ and $\psi$.
	\section{Maximum theoretical efficiency}
		It was shown in \cite{oo} that maximal asymptotic capacity of clique networks is $\log 2$. We generalise this result to multipartite cliques.

@@

		Fixing $k^* = -\frac{a^2}{2} \log_2 (d)$ gives us $P_{\exists e}$ and $\eta \sim \log_2 d \log_2 (1-d) \log 2$ and therefore \[\eta_{max} = \log 2\]

@@

	%Marche mieux pour de petits c --> le faire sur le sparse ?
